---
title: "metrics calculator"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Function to generate metrics for a setup

This function generates a bunch of metrics based on the data in the src files. These metrics can be used for selecting games, but also kept in mind when evaluating games played (as too easy or too hard).

Card data follow a rough model, trying to put numbers or qualifiers on card characteristics. Approximations are often used. There may be errors and inconsistencies. Metadata can be found in the xlsx files.

```{r metricsFun}
metricsGen = function(games,nr) {

  #games is a list of generated setups
  #nr is the element of that list to calculate metrics for
  
  #initialize metrics df
  bCount = 0
  metrics = tibble(bCount)
  
  ##colorcounts
  #issue if t or split cards with the same color
  #does not take into account villains gained as heroes
  metrics$bCount = 
    sum(games[[nr]]$scores$heroes$B*
          games[[nr]]$scores$heroes$Ct)
  metrics$rCount = 
    sum(games[[nr]]$scores$heroes$R*
          games[[nr]]$scores$heroes$Ct)
  metrics$yCount = 
    sum(games[[nr]]$scores$heroes$Y*
          games[[nr]]$scores$heroes$Ct)
  metrics$gCount = 
    sum(games[[nr]]$scores$heroes$G*
          games[[nr]]$scores$heroes$Ct)
  metrics$sCount = 
    sum(games[[nr]]$scores$heroes$S*
          games[[nr]]$scores$heroes$Ct)
  
  ##count color requirements of heroes, villains, mm and scheme
  #does not differentiate right now for epic, so slight inflation possible
  #might also consider ignoring if both sides of transforming mm care about a certain color
  metrics$bReq = 
    sum(games[[nr]]$scores$heroes$Br*
          games[[nr]]$scores$heroes$Ct) +
    sum(games[[nr]]$scores$villains$B*
          games[[nr]]$scores$villains$Ct) +
    sum(games[[nr]]$scores$mastermind$B) +
    games[[nr]]$scores$scheme$B
  metrics$rReq = 
    sum(games[[nr]]$scores$heroes$Rr*
          games[[nr]]$scores$heroes$Ct) +
    sum(games[[nr]]$scores$villains$R*
          games[[nr]]$scores$villains$Ct) +
    sum(games[[nr]]$scores$mastermind$R) +
    games[[nr]]$scores$scheme$R
  metrics$yReq = 
    sum(games[[nr]]$scores$heroes$Yr*
          games[[nr]]$scores$heroes$Ct) +
    sum(games[[nr]]$scores$villains$Y*
          games[[nr]]$scores$villains$Ct) +
    sum(games[[nr]]$scores$mastermind$Y) +
    games[[nr]]$scores$scheme$Y
  metrics$gReq = 
    sum(games[[nr]]$scores$heroes$Gr*
          games[[nr]]$scores$heroes$Ct) +
    sum(games[[nr]]$scores$villains$G*
          games[[nr]]$scores$villains$Ct) +
    sum(games[[nr]]$scores$mastermind$G) +
    games[[nr]]$scores$scheme$G
  metrics$sReq = 
    sum(games[[nr]]$scores$heroes$Sr*
          games[[nr]]$scores$heroes$Ct) +
    sum(games[[nr]]$scores$villains$S*
          games[[nr]]$scores$villains$Ct) +
    sum(games[[nr]]$scores$mastermind$S) +
    games[[nr]]$scores$scheme$S
  
  ###cost requirements
  #C2 and C4
  metrics$C2r = sum(games[[nr]]$scores$heroes$C2*
                      games[[nr]]$scores$heroes$Ct)
  metrics$C2 = sum(filter(games[[nr]]$scores$heroes,C==2)$Ct)
  
  metrics$C4r = sum(games[[nr]]$scores$heroes$C4*
                      games[[nr]]$scores$heroes$Ct)
  metrics$C4 = sum(filter(games[[nr]]$scores$heroes,C==4)$Ct)

  ##cost diversity
  metrics$Cdivr = sum(games[[nr]]$scores$heroes$CD*
                      games[[nr]]$scores$heroes$Ct)
  cost_div = games[[nr]]$scores$heroes %>%
    group_by(C) %>%
    summarize(sum = sum(Ct))
  #using fractions for Shannon and evenness calculations
  cost_div$p = cost_div$sum/sum(cost_div$sum)
  metrics$Cdiv = -sum(cost_div$p*log(cost_div$p))
  metrics$CdivEV = metrics$Cdiv/log(dim(cost_div)[1])

  ##spectrum
  metrics$colorDIVr = sum(games[[nr]]$scores$heroes$SP*
                            games[[nr]]$scores$heroes$Ct)
  colors = c("B","R","Y","G","S")
  n = unlist(metrics[1:5])
  color_div = tibble(colors,n)
  color_div$p = color_div$n/sum(color_div$n)
  metrics$colorDIV = -sum(color_div$p*log(color_div$p))
  metrics$colorEV = metrics$colorDIV /log(dim(color_div)[1])
  
  ##Wounds
  metrics$wndsum = sum(games[[nr]]$scores$heroes$Wd*
                         games[[nr]]$scores$heroes$Ct) + 
    sum(games[[nr]]$scores$villains$Wnd*
          games[[nr]]$scores$villains$Ct) +
    games[[nr]]$scores$scheme$Wnd*games[[nr]]$scores$scheme$CT
  
  if (dim(games[[nr]]$scores$mastermind)[1]==5) {
    metrics$wndsum = metrics$wndsum +
      games[[nr]]$scores$mastermind$Wnd[1]*5 +
      sum(games[[nr]]$scores$mastermind$Wnd[2:5])
  }
  if (dim(games[[nr]]$scores$mastermind)[1]==6) {
    metrics$wndsum = metrics$wndsum +
      games[[nr]]$scores$mastermind$Wnd[1]*2.5 +
      games[[nr]]$scores$mastermind$Wnd[2]*2.5 +
      sum(games[[nr]]$scores$mastermind$Wnd[3:6])
  }
  
  ##KO heroes
  games[[nr]]$scores$heroes$KOng = 0
  games[[nr]]$scores$heroes$KOng[games[[nr]]$scores$heroes$KO==2] = 1
  
  games[[nr]]$scores$villains$KOng = 0
  games[[nr]]$scores$villains$KOng[games[[nr]]$scores$villains$KOH==2] = 1
  
  metrics$kohsum = sum(games[[nr]]$scores$heroes$KOng*
                         games[[nr]]$scores$heroes$Ct) + 
    sum(games[[nr]]$scores$villains$KOng*
          games[[nr]]$scores$villains$Ct) +
    games[[nr]]$scores$scheme$KOH*games[[nr]]$scores$scheme$CT
  
  if (dim(games[[nr]]$scores$mastermind)[1]==5) {
    metrics$kohsum = metrics$kohsum +
      games[[nr]]$scores$mastermind$KOH[1]*5 +
      sum(games[[nr]]$scores$mastermind$KOH[2:5])
  }
  if (dim(games[[nr]]$scores$mastermind)[1]==6) {
    metrics$kohsum = metrics$kohsum +
      games[[nr]]$scores$mastermind$KOH[1]*2.5 +
      games[[nr]]$scores$mastermind$KOH[2]*2.5 +
      sum(games[[nr]]$scores$mastermind$KOH[3:6])
  }
  
  ##crowding
  metrics$crwdsum = sum(games[[nr]]$scores$villains$CRWD*
          games[[nr]]$scores$villains$Ct) +
    games[[nr]]$scores$scheme$CRWD*games[[nr]]$scores$scheme$CT
  
  if (dim(games[[nr]]$scores$mastermind)[1]==5) {
    metrics$crwdsum = metrics$crwdsum +
      games[[nr]]$scores$mastermind$CRWD[1]*5 +
      sum(games[[nr]]$scores$mastermind$CRWD[2:5])
  }
  if (dim(games[[nr]]$scores$mastermind)[1]==6) {
    metrics$crwdsum = metrics$crwdsum +
      games[[nr]]$scores$mastermind$CRWD[1]*2.5 +
      games[[nr]]$scores$mastermind$CRWD[2]*2.5 +
      sum(games[[nr]]$scores$mastermind$CRWD[3:6])
  }
  
  ##hencko
  #metrics$hencko = sum(games[[nr]]$scores$henchmen$KO_HERO)
  
  ##wincon
  metrics$wincon = games[[nr]]$scores$scheme$EW
  metrics$wincon = plyr::revalue(metrics$wincon,c(
                                 "VE" = "Villains Escaped",
                                 "SE" = paste0(games[[nr]]$scores$scheme$EWH," escaped"),
                                 "WO" = "Wound stack runs out",
                                 "LT" = "Last or second to last twist",
                                 "HK" = "Heroes KO'd",
                                 "O"= "Other"),warn_missing = F)
  
  #MoFi
  metrics$MoFir = sum(games[[nr]]$scores$heroes$MF)
  metrics$MoFi = sum(filter(games[[nr]]$scores$heroes,MO==1,FI==1)$Ct)
  
  #NoRu
  metrics$NoRur = sum(filter(games[[nr]]$scores$heroes,NR==-1)$Ct)
  metrics$NoRu = sum(filter(games[[nr]]$scores$heroes,NR==1)$Ct)
  
  #Lightshow
  metrics$Lightshow = sum(filter(games[[nr]]$scores$heroes,LS!=0)$Ct*filter(games[[nr]]$scores$heroes,LS!=0)$LS)
  metrics$Lightshowr = sum(filter(games[[nr]]$scores$heroes,LS!=0)$Ct)/sum(games[[nr]]$scores$heroes$Ct)
  metrics$bDef = metrics$bCount - metrics$bReq
  metrics$rDef = metrics$rCount - metrics$rReq
  metrics$gDef = metrics$gCount - metrics$gReq
  metrics$yDef = metrics$yCount - metrics$yReq
  metrics$sDef = metrics$sCount - metrics$sReq
  return(metrics)
}
```

## List the metrics for a list of games

This chunk sums up the metrics for the setups generated in the previous chunk.

```{r metrics}
#initiate metrics
for (j in 1:numberofruns) {
  games[[j]]$metrics = metricsGen(games,j)
}

metrics = games[[1]]$metrics
for (j in 2:numberofruns) {
  metrics = rbind(metrics,games[[j]]$metrics)
}



```